\documentclass{report}
\usepackage[a4paper, total={7.5in, 10in}]{geometry}
\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{multicol}
\usepackage{thmtools}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tipa}
\usepackage{array, makecell, cellspace}
\usepackage{bigints}
\usepackage[export]{adjustbox}
\usepackage{accents}
\setlength{\cellspacetoplimit}{13.2ex}
\setlength{\cellspacebottomlimit}{13.2ex}

\usepackage{ifxetex}

\ifxetex
    \usepackage{substitutefont}
    \substitutefont{T3}{\rmdefault}{cmr}
\fi

\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Georgia}

\title{Praktis 8\\Probability Distribution}
\author{Melvin Chia}

\newcommand\perm[2][^n]{\prescript{#1\mkern-2.5mu}{}P_{#2}}
\newcommand\permtwo[2][^n]{{}_{#1}P_{#2}}
\newcommand\comb[2][^n]{{}_{#1}C_{#2}}
\newcommand\combtwo[2][^n]{\prescript{#1\mkern-2.5mu}{}C_{#2}}
\renewcommand{\vec}[1]{\underaccent{\tilde}{#1}}

\newcommand{\sol}[1]{

    \noindent \textbf{Sol.}
}
\newcommand{\prooff}[1]{

    \noindent \textbf{Proof.}
}

\newcommand{\arc}[1]{{%
            \setbox9=\hbox{#1}%
            \ooalign{\resizebox{\wd9}{\height}{\texttoptiebar{\phantom{A}}}\cr#1}}}

\def\eos{\quad\hbox{\rlap{\hbox{\vrule depth 1.5pt height 2.6mm width 0.2mm \hskip 1mm \vrule height 2.6mm width 0.2mm}}{\vbox{\hrule height 0.2mm width 1.4mm \vskip 2.8mm \hrule depth 1.5pt height -0.35mm width 1.2mm}}}}

\counterwithout{equation}{chapter}
\setlength{\columnseprule}{1pt}
\setlength{\columnsep}{24pt}
\hfuzz=100pt
\setcounter{chapter}{8}

\begin{document}
\maketitle

\begin{multicols*}{2}
    \noindent\Large{\underline{\textbf{Praktis Formatif}}}
    \normalsize
    \section{Random Variable}
    \begin{enumerate}
        \item State the random variable for each of the following situations.
              \begin{enumerate}
                  \item In an in vitro fertilization (IVF) procedure, mature ova are successfully
                        collected from Puan Amy's ovaries to be fertilized by her husband's sperms.

                  \item The nurse takes the body temperature of the dengue fever patient every hour.

                  \item The daily attendance of the students in school must be recorded before 9 a.m.
              \end{enumerate}

        \item Identify whether the random variable in each of the following situations is a
              discrete random variable or a continuous random variable. Write all the
              possible outcomes in set notations.
              \begin{enumerate}
                  \item The time allocated to answer 10 questions of an online quiz is 1 hour. $X$ is
                        the random variable that represents the average time taken by all the students
                        to answer the questions. It is known that the minimum time taken is 40 minutes.

                  \item Five letters are chosen randomly from the word POSTMAN. $X$ is the random
                        variable that represents the number of consonants chosen.
              \end{enumerate}

        \item For each of the following situations,
              \begin{enumerate}
                  \item list all the possible outcomes for the random variable $X$ in a set notation,

                  \item draw a tree diagram that represents all the possible outcomes,

                  \item determine the probability distribution for $X$.

                        \begin{enumerate}
                            \item In a piano test the students are required to listen and state the 4 basic notes
                                  played by the teacher. $X$ is the random variable that represents the correct
                                  answers.

                            \item A piece of coin is tossed twice. $X$ is the random variable that represents the
                                  number of heads obtained.

                            \item Two fair dice are thrown simultaneously twice. $X$ is the random variable that
                                  represents the number of getting 4 as the difference in value between the
                                  numbers on the surface of each dice.
                        \end{enumerate}
              \end{enumerate}

        \item 3 camping lamps are chosen randomly from a bpx containing 12 damping lamps and checked. It is known that 30\% of camping lamps contained in a box are defective. $X$ is the random variable that represents the number of defective camping lamps chosen.
              \begin{enumerate}
                  \item Build a table of probability distribution for random variable $X$.
                  \item Draw a graph of probability distribution for $X$.
              \end{enumerate}

        \item $X$ is the number of baby girls in a twin's pregnancy. List all the possible outcomes for $X$ and determine whether it is a discrete or a continuous random variable. Give your reasons.

        \item The following diagram shows the graph of probability distribution of random
              variable $X$.
              \begin{enumerate}
                  \item State the type of random variable $X$.
                  \item Write all the outcomes for $X$ in the set notation.
                  \item Find teh value of $m$.
              \end{enumerate}

        \item Is the distribution in each of the following situations a binomial
              distribution? Explain.
              \begin{enumerate}
                  \item There are 2 red balls and 4 black balls in a box. A ball is randomly draw from
                        the box, the colour is recorded and returned before the next ball is drawn,
                        This process is repeated 4 times.

                  \item There are 2 red balls and 4 black balls in a box. Two balls are draw
                        simultaneously from the box.

                  \item A supermarket holds a lucky draw activity for the customers. The following
                        diagram shows the wheel of dream used to decide the lucky draw prizes to be
                        won. Rahman has spent more than RM300 and is entitled to spin the wheel 3
                        times.
              \end{enumerate}

        \item During the Movement Control Order (MCO), it is found that the attendance of
              students of a school for all the online lessons is 85\%. If 10 students are
              chosen at random from the school, find the probability that
              \begin{enumerate}
                  \item all students attended all the online lessons,
                  \item at least 8 students attended all the online lessons.
              \end{enumerate}

        \item In a survey, it is found that 5\% of the residents do not own a car. If 8
              residents are chosen, find the probability that
              \begin{enumerate}
                  \item 2 residents do not own a car,
                  \item more than 2 residents own at least a car.
              \end{enumerate}

        \item The probability to win a gram is 0.6.
              \begin{enumerate}
                  \item If 5 games are played by Aiman, find the probability that he wins at least 2
                        games.

                  \item If $m$ games are played, the probability to win 1 game is 5 times the
                        probability to lose in all games. Find the value of $m$.
              \end{enumerate}

        \item The probability of one who puts on the face mask properly being tested positive
              with COVID-19 is $p$. 10 people are randomly chosen to carry out the COVID-19
              swab test. It is found that the probability of nobody being tested positive
              with the COVID-19 virus is $0.9044$, find
              \begin{enumerate}
                  \item the value of $p$,
                  \item the probability that 2 people who put on the mask properly being tested
                        positive with the COVID-10 virus.
              \end{enumerate}

        \item Solve each of the following situations.
              \begin{enumerate}
                  \item The probability of children who take the eyesight test and found the be
                        short-sighted is $\dfrac{4}{5}$. If 500 children took the eyesight test in a
                        particular week, find the expected number of children who are short-sighted.
                        Hence, find the variance and the standard deviation.

                  \item There are 20 questions in a test. Every question has four choices of answers
                        and there is only one correct answer. Billy chooses the answers randomly.
                        Calculate the mean and the standard deviation of his score.
              \end{enumerate}
    \end{enumerate}

\end{multicols*}

\end{document}