\documentclass{report}
\usepackage[a4paper, total={7.5in, 10in}]{geometry}
\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{multicol}
\usepackage{thmtools}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tipa}
\usepackage{array, makecell, cellspace}
\usepackage{bigints}
\usepackage[export]{adjustbox}
\usepackage{accents}
\setlength{\cellspacetoplimit}{13.2ex}
\setlength{\cellspacebottomlimit}{13.2ex}

\usepackage{ifxetex}

\ifxetex
    \usepackage{substitutefont}
    \substitutefont{T3}{\rmdefault}{cmr}
\fi

\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Georgia}

\title{Praktis 8\\Progressions}
\author{Melvin Chia}

\newcommand\perm[2][^n]{\prescript{#1\mkern-2.5mu}{}P_{#2}}
\newcommand\permtwo[2][^n]{{}_{#1}P_{#2}}
\newcommand\comb[2][^n]{{}_{#1}C_{#2}}
\newcommand\combtwo[2][^n]{\prescript{#1\mkern-2.5mu}{}C_{#2}}
\renewcommand{\vec}[1]{\underaccent{\tilde}{#1}}

\newcommand{\sol}[1]{

    \noindent \textbf{Sol.}
}
\newcommand{\prooff}[1]{

    \noindent \textbf{Proof.}
}

\newcommand{\arc}[1]{{%
            \setbox9=\hbox{#1}%
            \ooalign{\resizebox{\wd9}{\height}{\texttoptiebar{\phantom{A}}}\cr#1}}}

\def\eos{\quad\hbox{\rlap{\hbox{\vrule depth 1.5pt height 2.6mm width 0.2mm \hskip 1mm \vrule height 2.6mm width 0.2mm}}{\vbox{\hrule height 0.2mm width 1.4mm \vskip 2.8mm \hrule depth 1.5pt height -0.35mm width 1.2mm}}}}

\counterwithout{equation}{chapter}
\setlength{\columnseprule}{1pt}
\setlength{\columnsep}{24pt}
\hfuzz=100pt
\setcounter{chapter}{8}

\begin{document}
\maketitle

\begin{multicols*}{2}
    \noindent\Large{\underline{\textbf{Praktis Formatif}}}
    \normalsize
    \section{Arithmetic Progressions}

    \begin{enumerate}
        \item Given that the first three terms of an arithmetic progression are 4, 11, and
              18. Find
              \begin{enumerate}
                  \item the common difference of this progression,
                  \item the value of the $13^{th}$ term.
              \end{enumerate}

        \item The first three terms of an arithmetic progression are 63, 59, and 55. Find the
              least value of $n$ such that the $n^{th}$ term of this progression is negative.

        \item Given that the seventh term of an arithmetic progression is twice of the second
              term and the $11^{th}$ term is 21. Find the first term and the common
              difference.

        \item \begin{enumerate}
                  \item Find the number of multiples of 17 between 300 and 500.

                  \item Hence, find the sum of all multiples of 17 between 300 and 500.
              \end{enumerate}

        \item The first three terms of an arithmetic progression are $x-2$, $2x-1$ and
              $4x-7$. Find
              \begin{enumerate}
                  \item the value of $x$,
                  \item the sum of the next 8 terms.
              \end{enumerate}
    \end{enumerate}

\end{multicols*}

\end{document}