\chapter{Indefinite Integrals}

\section{Indefinite Integrals as the Inverse of Differentiation}

Let function $F(x)$ and $f(x)$ be defined at the interval $(a, b)$. If any
point $x$ in this interval satisfies $F'(x) = f(x)$, then $F(x)$ is is the
preimage of $f(x)$ at the interval $(a, b)$.

According to the definition above, to find the preimage of a function $f(x)$,
we need to find the function $F(x)$ that satisfies $F'(x) = f(x)$. For example,
\begin{flalign*}
    (x^2)'     & = 2x   & \\
    (x^2 + 1)' & = 2x   & \\
    (x^2 - 2)' & = 2x   & \\
               & \vdots
\end{flalign*}

For any constant $C$, the derivative of $x^2 + C$ is $2x$. Hence, the preimage
of $2x$ is $x^2 + C$, where $C$ is an arbitary constant.

Since $\left[F(x) + C\right]' = F'(x) + 0 = F'(x)$, if the function $F(x)$ is a
preimage of $f(x)$, then $F(x) + C$ (C is a constant) is also a preimage of
$f(x)$. That is to say, there are infinite number of preimages of a function
$f(x)$.

In the other hand, if $F(x)$ and $G(x)$ are both preimages of $f(x)$, then
$F'(x) = f(x)$, $G'(x) = f(x)$.
\begin{flalign*}
    \because\ \left[G(x) - F(x)\right]' & = G'(x) - F'(x) & \\
                                        & = f(x) - f(x)   & \\
                                        & = 0
\end{flalign*}
\vspace{-3em}
\begin{flalign*}
    \therefore\ G(x) - F(x) & = C        & \\
    \text{i.e.}\ G(x)       & = F(x) + C
\end{flalign*}
This shows that for any two preimages of $f(x)$, the difference between them is a constant. If $F(x)$ is a preimage of $f(x)$, then all the preimages of $f(x)$ can be expressed as $F(x) + C$, where $C$ is a constant.
\subsection*{The Concept of Indefinite Integral}
Let function $F(x)$ be a preimage of $f(x)$. All the preimages $F(x) + C$ ($C$
is a constant) of a function $f(x)$ is called the indefinite integral of
$f(x)$, denoted by $\displaystyle\int f(x)dx$, i.e. $\displaystyle\int f(x)dx =
    F(x) + C$. $\displaystyle\int$ is called the integral sign, $f(x)$ is called
the integrand, $C$ is called the constant of integration.

Finding the indefinite integral of a function $f(x)$ is equivalent to finding
all the preimages of $f(x)$. From the explanation above, we just need to find
one preimage of $f(x)$, then add a constant $C$ to it to get the indefinite
integral of $f(x)$.

\section{Arithmetic Properties of Indefinite Integrals}

\subsection*{Basic Formulas of Indefinite Integrals}

In order to learn the methods and skills of finding indefinite integrals, we
must first learn some basic formulas of indefinite integrals. We know that
finding the indefinite integral is equivalent to finding the anti-derivative.
Therefore, we can get the formulas of indefinite integrals from the
corresponding formulas of derivatives.

For example, when $n \neq -1$, $\dfrac{d}{dx}\left(\dfrac{x^{n+1}}{n+1}\right)
    = x^n$.

Hence, $\displaystyle\int x^{n}dx = \dfrac{x^{n+1}}{n+1} + C$.

Similarly, we can also get the other basic formulas of indefinite integrals.
The basic formulas of indefinite integrals are listed below:
\begin{center}
    \framebox{
        \parbox[t][6cm]{12cm}{ \addvspace{0.2cm} \centering \begin{multicols}{2}
                \begin{enumerate}[label = ]
                    \item $\displaystyle\int x^{n}dx = \dfrac{x^{n+1}}{n+1} + C$, $n \neq -1$
                    \item $\displaystyle\int e^{x}dx = e^{x} + C$
                    \item $\displaystyle\int \sin xdx = -\cos x + C$
                    \item $\displaystyle\int \sec^2xdx = \tan x + C$
                    \item $\displaystyle\int \csc x\cot xdx = -\csc x + C$
                    \item $\displaystyle\int \dfrac{1}{x}dx = \ln|x| + C$
                    \item $\displaystyle\int a^{x}dx = \dfrac{a^x}{\ln a} + C$,
                    \item $\displaystyle\int \cos xdx = \sin x + C$
                    \item $\displaystyle\int \csc^2xdx = -\cot x + C$
                    \item $\displaystyle\int \sec x\tan xdx = \sec x + C$
                \end{enumerate}
            \end{multicols} }}
\end{center}
\vspace{0.9em}

\input{exercises/Chapter 27/Practice 1.tex}
\input{exercises/Chapter 27/Exercise 27.2a.tex}

Using the arithmetic properties of derivatives, we can also get the following
arithmetic properties of indefinite integrals:
\begin{center}
    \framebox{
        \parbox[t][2.6cm]{12cm}{ \addvspace{0.2cm} \centering \begin{enumerate}
                \item Constant Multiple Rule: $\displaystyle\int kf(x)dx = k\int f(x)dx$, where $k$
                      is a constant.
                \item Sum and Difference Rule: $\displaystyle\int \left[f(x) \pm g(x)\right]dx = \int
                          f(x)dx \pm \int g(x)dx$
            \end{enumerate} }}
\end{center}
\vspace{0.9em}

Note that when integrating by parts, the result of each part of the integral
contains a constant of integration. However, the sum (or difference) of
multiple constants of integration is still a constant of integration.
Therefore, when integrating by parts, we only need to add one constant of
integration to the final result.

\input{exercises/Chapter 27/Practice 2.tex}

\newpage
\input{exercises/Chapter 27/Practice 3.tex}
\input{exercises/Chapter 27/Exercise 27.2b.tex}

\section{Integration by Substitution}

In the last section, we learned to find the indefinite integral of some
functions using some basic formulas of indefinite integrals and two arithmetic
properties of indefinite integrals. However, for the indefinite integral of
some more complicated functions like $\displaystyle\int 3\sqrt{3x + 1}dx$,
$\displaystyle\int 2\sin2xdx$, etc., we cannot find their indefinite integrals
straight away using the basic formulas of indefinite integrals and the
arithmetic properties of indefinite integrals. Hence, we need to learn some
other methods to find the indefinite integral of these functions. Here we will
introduce a method called integration by substitution.

Consider a function $F(u)$, where $u$ is a function of $x$, i.e. $u = g(x)$.

Using the chain rule, we have $\dfrac{d}{dx}F\left(g(x)\right) =
    F'\left(g(x)\right) \cdot g'(x)$. Hence,
\begin{center}
    \framebox{
        \parbox[t][1.2cm]{6cm}{ \addvspace{0.2cm} \centering $\displaystyle\int
                F'\left(g(x)\right) \cdot g'(x)dx = F\left(g(x)\right) + C$ }}
\end{center}
\vspace{0.9em}
Generally speaking, during the calculation process, we let $u = g(x)$.
\begin{flalign*}
    \therefore\ \displaystyle\int F'\left(g(x)\right) \cdot g'(x)dx & = \int F'(u)\dfrac{du}{dx}dx & \\
                                                                    & = \int F'(u)du               & \\
                                                                    & = F(u) + C                   & \\
                                                                    & = F\left(g(x)\right) + C
\end{flalign*}
For the functions that we cannot find their indefinite integrals straight away using the basic formulas of indefinite integrals, if it can be expressed in the form of $\displaystyle\int F'\left(g(x)\right) \cdot g'(x)dx$, we can perform substitution using $u = g(x)$ and express the indefinite integral as $\displaystyle\int F'(u)du$ to find its indefinite integral.

\input{exercises/Chapter 27/Practice 4.tex}
\input{exercises/Chapter 27/Exercise 27.3a.tex}

\newpage
\input{exercises/Chapter 27/Practice 5.tex}
\input{exercises/Chapter 27/Exercise 27.3b.tex}

\section{Integration by Partial Fractions}

Generally speaking, in order to find the indefinite integral of a proper
fraction, we first have to decompose the proper fraction into partial
fractions, then perform integration on each term. This method of integration is
called integration by partial fractions.

To find the partial fractions of an improper fraction, we can first decompose
the fraction into the sum of a polynomial and a proper fraction using
polynomial division.

\input{exercises/Chapter 27/Practice 6.tex}

\newpage

\input{exercises/Chapter 27/Exercise 27.4.tex}

\newpage
\section{Applications of Indefinite Integrals}

We can use derivative to find the slope of a tangent line to a curve at any
point on the curve. Conversely, if the slope of a tangent line to a curve at a
point on the curve is known, we can use indefinite integration to find the
equation of the curve.

\input{exercises/Chapter 27/Practice 7.tex}
\input{exercises/Chapter 27/Exercise 27.5.tex}

\newpage
\input{exercises/Chapter 27/Revision Exercise 27.tex}
